\Title

### 2015-08-24 moho-inversion.tex
Add SAm data and sed model figures
A few more words in methods intro

%\documentclass[]{article}
%\usepackage{natbib}
\documentclass[extra,mreferee]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

@@

@@

\noindent \textbf{Keywords:} \Keywords

@@

@@

We must first isolate the target anomalous density distribution.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the gravity\footnote{The term ``gravity''
refers the sum of the gravitational and centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the formula presented in \citet{li_ellipsoid_2001}.
The resulting quantity is known as the gravity disturbance,

@@

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and depth $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the mass excesses and deficiencies caused by differences between the real Moho
topography and the reference Moho ($z_{ref}$).
The last is what we are interested in.
All effects must either be removed or assumed negligible.
The input data for the inversion is assumed to be the isolated gravitational
effect of the anomalous Moho.

@@

Assume all other sources were removed.
Only Moho topography around a reference level.
\todo{Include figure of Moho with all else  removed.}
Discretize into tesseroids.
Parameters are the Moho depths.
Establish that the reference level ($h_{ref}$)  and density contrast
($\Delta\rho_j$) are hyper-parameters.

@@

Formulate regularized inversion using Gauss-Newton and Steepest Descent.
Use full Jacobian.

@@

%\begin{figure}
    %\centering
    %\includegraphics[width=\columnwidth]{figures/figure}
    %\caption{This is a figure caption.}
    %\label{fig:myfig}
%\end{figure}

@@

>>>>

%\documentclass[]{article}
%\usepackage{natbib}
%\documentclass[extra,mreferee]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

@@

% Useful commands
% ===============
\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\figs}[2]{Figs.\ref{fig:#1}-\ref{fig:#2}}
\newcommand{\subfig}[2]{Fig.~\ref{fig:#1}#2}
\newcommand{\subfigs}[3]{Figs.\ref{fig:#1}#2-\ref{fig:#1}#3}
\newcommand{\eq}[1]{Eq.~\ref{eq:#1}}
\newcommand{\eqs}[2]{Eqs.~\ref{eq:#1}-\ref{eq:#2}}

@@

@@

\noindent\textbf{Key words:} \Keywords

@@

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
gravity\footnote{The term ``gravity'' refers the sum of the gravitational and
centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the closed-form solution presented in \citet{li_ellipsoid_2001}.
The resulting quantity is known as the gravity disturbance,

@@

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the mass excesses and deficiencies caused by differences between the real Moho
topography and the reference Moho ($z_{ref}$).
The latter is what we are interested in.
In order to invert for the Moho topography, all effects must either be removed
or assumed negligible.
The gravitational effects of topography and sedimentary basins is
removed using the models
ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
\citep{amante_c._and_b._w._eakins_etopo1_2009}
and CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}}
\citep{laske_update_2013}.
Lateral variations in density along the Moho cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in the South American and African continents.

@@

We parameterize the forward problem by discretizing the Moho undulation around
the reference depth into tesseroids.

Only Moho topography around a reference level.
\todo{Include figure of Moho with all else  removed.}
Discretize into tesseroids.
Parameters are the Moho depths.
Establish that the reference level ($h_{ref}$)  and density contrast
($\Delta\rho_j$) are hyper-parameters.

@@

Formulate regularized inversion using Gauss-Newton and Steepest Descent.
Use full Jacobian.
Steepest has poor convergence when close to the solution
\citep{kelley_iterative_1987}.

@@

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
    \caption{This is a figure caption.}
    \label{fig:sam-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
    \caption{This is a figure caption.}
    \label{fig:sam-sed}
\end{figure*}

\fig{sam-data}, \figs{sam-data}{sam-sed}, \subfigs{sam-data}{a}{f}.
